Stay in shape! Homework exam II

### 2016-04-03 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
fixed temporal analysis.

When we traverse the tree we spend at most $O(1+r_v)$ time at
that node $v$ where $r_v$ is the time spend reporting the results.
Summing over all $r_v$ results in $r$. The depth of the main tree
is $log(n)$. we visit at most two nodes at any depth of the tree.
This results in:

\[ 2\cdot (log(n)+r)\]

time to traverse it. Now we will fill in R by analysing the
inner tree. At any node $v$ we visit we spend $O(1+k_v)$ time where
$k_v$ is the number of linesegments we report at $v$. Summing
over $k_v$ results in $k$. The depth of the tree is $log(n)$,
we visit at most one node at any depth of the tree. This results in:

@@

So now we can fill in $r$:

\[ 2\cdot (log(n)+log(n)+k)\]

Which results in:

\[ O(log(n)+k) \]

query time.
\section{Voronoi nearest neigbour\emph{s}}
\subsection{Storage}
\subsection{Query time}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.

>>>>

We'll start by analysing the inner tree.
At any node $v$ we visit we spend $O(1+k_v)$ time where
$k_v$ is the number of linesegments we report at $v$. Summing
over $k_v$ results in $k$. The depth of the tree is $log(n)$,
we visit at most one node at any depth of the tree. This results in:

@@

So in the main tree we spend $O(log(n)+r_v)$ per call, where $r_v$ is
the result for node $v$. Its also worth noting that we visit each level
of the tree a maximum two times. Hence the total time we spend is:

\[ 2\cdot \sum_v(log(n)+r_v)\]

Notice that $\sum_v r_v = r$ and that the search path of $y$ and $y'$
in the main tree have depth $log(n)$. so $\sum_v O(log(n))=log^2(n)$.
Which results in:

\[ O(log^2(n)+r) \]

\section{Voronoi nearest neigbour\emph{s}}
\subsection{Storage}
\subsection{Query time}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.
